\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-17 manuscript.Rmd
* table 1 updated

---
nocite: |
  `r cite_r("references.bib")`
  [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
  [@horne1976self][@roenneberg2003life][@Olivier.2016][@buysse1989pittsburgh][@Xie.2021]
  [@Wu.2017]
---

@@

```{r results='asis'}
relevant.scale.data %>%
   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1:4, width = "4cm")
```

@@

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. For our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one making it a 5 point Likert type response format. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]. We confirmed the latent structure obtained in the EFA by conducting a "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV). We estiablished the measurement invariance of our tool across native and non-native English speakers using structural equation model framework. To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic]. Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:EFATableAppB)) and rejected the latent structure obtained as the factors were less interpretable.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Figure \@ref(fig:EFAplot) depicts the obtained five-five factor structure. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table \@ref(tab:sixFacTab)).

>>>>

---
nocite: |
  `r cite_r("references.bib")`
  [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
  [@horne1976self][@roenneberg2003life][@Olivier.2016][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita]
---

@@

```{r results='asis'}
relevant.scale.data %>%
   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1:6, width = "2cm")
```

@@

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one, making it a 5 point Likert type response format. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]. We confirmed the latent structure obtained in the EFA by conducting a categorical "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV). We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework. To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic]. Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:EFATableAppB)) and rejected the latent structure obtained as the factors were less interpretable.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (<.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Table \@ref(tab:MinResTab)). Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients. The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`. Figure \@ref(fig:EFAplot) depicts the obtained five-five factor structure. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring. [@desjardinsHandbookEducationalMeasurement2018]. Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table \@ref(tab:sixFacTab)).
